\bibitem{vapnik1971uniform} Vapnik, Vladimir N, Chervonenkis, Alexey Y. On the uniform convergence of relative frequencies of events to their probabilities. Theory of Probability and its Applications. V.~16, N~2. P.~264--280. 1971.
\bibitem{valiant1984theory} Valiant, Leslie G. A theory of the learnable. Communications of the ACM. V.~27, N~11. P.~1134--1142. 1984.
\bibitem{blumer1989learnability} Blumer, Anselm, Ehrenfeucht, Andrzej, Haussler, David, Warmuth, Manfred K. Learnability and the Vapnik-Chervonenkis dimension. Journal of the ACM. V.~36, N~4. P.~929--965. 1989.
\bibitem{bartlett2002rademacher} Bartlett, Peter L, Mendelson, Shahar. Rademacher and Gaussian complexities: Risk bounds and structural results. Journal of Machine Learning Research. V.~3. P.~463--482. 2002.
\bibitem{kolmogorov1961epsilon} Kolmogorov, Andrey N, Tikhomirov, Vladimir M. $\varepsilon$-entropy and $\varepsilon$-capacity of sets in functional spaces. Uspekhi Matematicheskikh Nauk. V.~16, N~2. P.~3--86. 1961.
\bibitem{cybenko1989approximation} Cybenko, George. Approximation by superpositions of a sigmoidal function. Mathematics of Control, Signals and Systems. V.~2, N~4. P.~303--314. 1989.
\bibitem{hornik1989multilayer} Hornik, Kurt, Stinchcombe, Maxwell, White, Halbert. Multilayer feedforward networks are universal approximators. Neural Networks. V.~2, N~5. P.~359--366. 1989.
\bibitem{russo2016controlling} Russo, Daniel, Zou, James. Controlling bias in adaptive data analysis using information theory. Advances in Neural Information Processing Systems. V.~29. 2016.
\bibitem{xu2017information} Xu, Aolin, Raginsky, Maxim. Information-theoretic analysis of generalization capability of learning algorithms. Advances in Neural Information Processing Systems. V.~30. 2017.
\bibitem{bousquet2002stability} Bousquet, Olivier, Elisseeff, Andre. Stability and generalization. Journal of Machine Learning Research. V.~2. P.~499--526. 2002.
\bibitem{mcallester1999pac} McAllester, David A. Some PAC-Bayesian theorems. Machine Learning. V.~37, N~3. P.~355--363. 1999.
\bibitem{dziugaite2017computing} Dziugaite, Gintare Karolina, Roy, Daniel M. Computing nonvacuous generalization bounds for deep (stochastic) neural networks with many more parameters than training data. Uncertainty in Artificial Intelligence. 2017.
\bibitem{hestness2017deep} Hestness, Joel, Narang, Sharan, Ardalani, Newsha, Diamos, Gregory, Jun, Heewoo, Kianinejad, Hassan, Patwary, Mostofa, Yang, Yang, Zhou, Yanqi. Deep Learning Scaling is Predictable, Empirically. arXiv preprint arXiv:1712.00409. 2017.
\bibitem{kaplan2020scaling} Kaplan, Jared, McCandlish, Sam, Henighan, Tom, Brown, Tom B, Chess, Benjamin, Child, Rewon, Gray, Scott, Radford, Alec, Wu, Jeffrey, Amodei, Dario. Scaling laws for neural language models. arXiv preprint arXiv:2001.08361. 2020.
\bibitem{vapnik1998statistical} Vapnik, Vladimir N. Statistical Learning Theory. Wiley. 1998.
\bibitem{vorontsov2004combinatorial} Воронцов, Константин В. Комбинаторный подход к оценке качества обучаемых алгоритмов. Математические вопросы кибернетики. V.~13. P.~5--51. 2004.
\bibitem{anthony1999neural} Anthony, Martin, Bartlett, Peter L. Neural Network Learning: Theoretical Foundations. Cambridge University Press. 1999.
\bibitem{kearns1994introduction} Kearns, Michael J, Vazirani, Umesh V. An Introduction to Computational Learning Theory. MIT Press. 1994.
\bibitem{shalev2014understanding} Shalev-Shwartz, Shai, Ben-David, Shai. Understanding Machine Learning: From Theory to Algorithms. Cambridge University Press. 2014.
\bibitem{koltchinskii2001rademacher} Koltchinskii, Vladimir. Rademacher penalties and structural risk minimization. IEEE Transactions on Information Theory. V.~47, N~5. P.~1902--1914. 2001.
\bibitem{dudley1978central} Dudley, Richard M. Central limit theorems for empirical measures. Annals of Probability. V.~6, N~6. P.~899--929. 1978.
\bibitem{pollard1984convergence} Pollard, David. Convergence of Stochastic Processes. Springer. 1984.
\bibitem{dudley1999uniform} Dudley, Richard M. Uniform Central Limit Theorems. Cambridge University Press. 1999.
\bibitem{van1996weak} van der Vaart, Aad W, Wellner, Jon A. Weak Convergence and Empirical Processes: With Applications to Statistics. Springer. 1996.
\bibitem{ledoux2001concentration} Ledoux, Michel. The Concentration of Measure Phenomenon. American Mathematical Society. 2001.
\bibitem{tishby1999information} Tishby, Naftali, Pereira, Fernando C, Bialek, William. The information bottleneck method. arXiv preprint physics/0004057. 1999.
\bibitem{shamir2010learnability} Shamir, Ohad, Sabato, Sivan, Tishby, Naftali. Learnability and stability in the general learning setting. Conference on Learning Theory. P.~463--482. 2010.
\bibitem{negrea2019information} Negrea, Jeffrey, Haghifam, Mahdi, Dziugaite, Gintare Karolina, Khisti, Ashish, Roy, Daniel M. Information-Theoretic Generalization Bounds for SGLD via Data-Dependent Estimates. Advances in Neural Information Processing Systems. V.~32. 2019.
\bibitem{li2020understanding} Li, Jingling, Sun, Yanchao, Su, Jiahao, Suzuki, Taiji, Huang, Furong. Understanding Generalization in Deep Learning via Tensor Methods. Proceedings of the Twenty Third International Conference on Artificial Intelligence and Statistics. V.~108. P.~504--515. PMLR. 2020.
\bibitem{hoffman2013stochastic} Hoffman, Matthew D, Blei, David M, Wang, Chong, Paisley, John. Stochastic variational inference. Journal of Machine Learning Research. V.~14, N~1. P.~1303--1347. 2013.
\bibitem{seeger2002pac} Seeger, Matthias. PAC-Bayesian generalisation error bounds for Gaussian process classification. Journal of Machine Learning Research. V.~3. P.~233--269. 2002.
\bibitem{catoni2007pac} Catoni, Olivier. PAC-Bayesian Supervised Classification: The Thermodynamics of Statistical Learning. Institute of Mathematical Statistics. 2007.
\bibitem{vaswani2017attention} Vaswani, Ashish, Shazeer, Noam, Parmar, Niki, Uszkoreit, Jakob, Jones, Llion, Gomez, Aidan N, Kaiser, Lukasz, Polosukhin, Illia. Attention is all you need. Advances in Neural Information Processing Systems. V.~30. 2017.
\bibitem{dong2021attention} Dong, Yihe, Cordonnier, Jean-Baptiste, Loukas, Andreas. Attention is not all you need: Pure attention loses rank doubly exponentially with depth. International Conference on Machine Learning. P.~2793--2803. 2021.
\bibitem{jacot2018neural} Jacot, Arthur, Gabriel, Franck, Hongler, Clement. Neural tangent kernel: Convergence and generalization in neural networks. Advances in Neural Information Processing Systems. V.~31. 2018.
\bibitem{soudry2018implicit} Soudry, Daniel, Hoffer, Elad, Nacson, Mor Shpigel, Gunasekar, Suriya, Srebro, Nathan. The implicit bias of gradient descent on separable data. Journal of Machine Learning Research. V.~19, N~1. P.~2822--2878. 2018.
\bibitem{ho2020denoising} Ho, Jonathan, Jain, Ajay, Abbeel, Pieter. Denoising diffusion probabilistic models. Advances in Neural Information Processing Systems. V.~33. P.~6840--6851. 2020.
\bibitem{song2021score} Song, Yang, Sohl-Dickstein, Jascha, Kingma, Diederik P, Kumar, Abhishek, Ermon, Stefano, Poole, Ben. Score-based generative modeling through stochastic differential equations. International Conference on Learning Representations. 2021.
\bibitem{li2018visualizing} Li, Hao, Xu, Zheng, Taylor, Gavin, Studer, Christoph, Goldstein, Tom. Visualizing the Loss Landscape of Neural Nets. Advances in Neural Information Processing Systems. V.~31. 2018.
\bibitem{hochreiter1997flat} Hochreiter, Sepp, Schmidhuber, Jurgen. Flat minima. Neural Computation. V.~9, N~1. P.~1--42. 1997.
\bibitem{kiselev2024unraveling} Kiselev, Nikita, Grabovoy, Andrey. Unraveling the Hessian: A Key to Smooth Convergence in Loss Function Landscapes. Doklady Mathematics. V.~110, N~S1. P.~S42. 2025.
\bibitem{sagun2017eigenvalues} Sagun, Levent, Bottou, Leon, LeCun, Yann. Eigenvalues of the Hessian in Deep Learning: Singularity and Beyond. arXiv preprint arXiv:1611.07476. 2017.
\bibitem{chaudhari2019entropy} Chaudhari, Pratik, Choromanska, Anna, Soatto, Stefano, LeCun, Yann, Baldassi, Carlo, Borgs, Christian, Chayes, Jennifer, Sagun, Levent, Zecchina, Riccardo. Entropy-SGD: Biasing gradient descent into wide valleys. Journal of Statistical Mechanics: Theory and Experiment. V.~2019, N~12. P.~124018. 2019.
\bibitem{pennington2017resurrecting} Pennington, Jeffrey, Schoenholz, Samuel S, Ganguli, Surya. Resurrecting the sigmoid in deep learning through dynamical isometry: theory and practice. Advances in Neural Information Processing Systems. V.~31. 2017.
\bibitem{belkin2019reconciling} Belkin, Mikhail, Hsu, Daniel, Ma, Siyuan, Mandal, Soumik. Reconciling modern machine-learning practice and the classical bias--variance trade-off. Proceedings of the National Academy of Sciences. V.~116, N~32. P.~15849--15854. 2019.
\bibitem{nakkiran2021deep} Nakkiran, Preetum, Kaplun, Gal, Bansal, Yamini, Yang, Tristan, Barak, Boaz, Sutskever, Ilya. Deep double descent: Where bigger models and more data hurt. Journal of Statistical Mechanics: Theory and Experiment. V.~2021, N~12. P.~124003. 2021.
\bibitem{arora2019fine} Arora, Sanjeev, Du, Simon, Hu, Wei, Li, Zhiyuan, Wang, Ruosong. Fine-grained analysis of optimization and generalization for overparameterized two-layer neural networks. International Conference on Machine Learning. P.~322--332. 2019.
\bibitem{chizat2019lazy} Chizat, Lenaic, Oyallon, Edouard, Bach, Francis. On lazy training in differentiable programming. Advances in Neural Information Processing Systems. V.~33. 2019.
\bibitem{woodworth2020kernel} Woodworth, Blake, Gunasekar, Suriya, Lee, Jason D., Moroshko, Edward, Savarese, Pedro, Golan, Itay, Soudry, Daniel, Srebro, Nathan. Kernel and Rich Regimes in Overparametrized Models. Proceedings of Thirty Third Conference on Learning Theory. V.~125. P.~3635--3673. PMLR. 2020.
\bibitem{hoffman2022training} Hoffmann, Jordan, Borgeaud, Sebastian, Mensch, Arthur, Buchatskaya, Elena, Cai, Trevor, Rutherford, Eliza, de Las Casas, Diego, Hendricks, Lisa Anne, Welbl, Johannes, Clark, Aidan, Hennigan, Tom, Noland, Eric, Millican, Katie, van den Driessche, George, Damoc, Bogdan, Guy, Aurelia, Osindero, Simon, Simonyan, Karen, Elsen, Erich, Vinyals, Oriol, Rae, Jack W., Sifre, Laurent. Training compute-optimal large language models. Proceedings of the 36th International Conference on Neural Information Processing Systems. Curran Associates Inc. 2022.
\bibitem{henighan2020scaling} Henighan, Tom, Kaplan, Jared, Katz, Mor, Chen, Mark, Hesse, Christopher, Jackson, Jacob, Jun, Heewoo, Brown, Tom B., Dhariwal, Prafulla, Gray, Scott, Hallacy, Chris, Mann, Benjamin, Radford, Alec, Ramesh, Aditya, Ryder, Nick, Ziegler, Daniel M., Schulman, John, Amodei, Dario, McCandlish, Sam. Scaling Laws for Autoregressive Generative Modeling. CoRR. V.~abs/2010.14701. 2020.
\bibitem{hardt2016train} Hardt, Moritz, Recht, Benjamin, Singer, Yoram. Train faster, generalize better: stability of stochastic gradient descent. Proceedings of the 33rd International Conference on Machine Learning. P.~1225--1234. 2016.
\bibitem{charles2017stability} Charles, Zachary, Papailiopoulos, Dimitris. Stability and Generalization of Learning Algorithms that Converge to Global Optima. Proceedings of the 35th International Conference on Machine Learning. V.~80. P.~745--754. PMLR. 2018.
\bibitem{kutin2002almost} Kutin, Samuel, Niyogi, Partha. Almost-everywhere algorithmic stability and generalization error. Proceedings of the Eighteenth Conference on Uncertainty in Artificial Intelligence. P.~275--282. 2002.
\bibitem{dwork2006calibrating} Dwork, Cynthia, McSherry, Frank, Nissim, Kobbi, Smith, Adam. Calibrating Noise to Sensitivity in Private Data Analysis. Theory of Cryptography. P.~265--284. Springer. 2006.
\bibitem{bassily2016algorithmic} Bassily, Raef, Nissim, Kobbi, Smith, Adam, Steinke, Thomas, Stemmer, Uri, Ullman, Jonathan. Algorithmic stability for adaptive data analysis. Proceedings of the Forty-Eighth Annual ACM Symposium on Theory of Computing. P.~1046--1059. 2016.
\bibitem{bottou2008tradeoffs} Bottou, Leon, Bousquet, Olivier. The Tradeoffs of Large Scale Learning. Advances in Neural Information Processing Systems. V.~20. 2007.
\bibitem{lei2020stability} Lei, Yunwen, Yang, Zhenhuan, Yang, Tianbao, Ying, Yiming. Stability and Generalization of Stochastic Gradient Methods for Minimax Problems. arXiv preprint arXiv:2105.03793. 2021.
\bibitem{shalev2010learnability} Shalev-Shwartz, Shai, Shamir, Ohad, Srebro, Nathan, Sridharan, Karthik. Learnability, Stability and Uniform Convergence. Journal of Machine Learning Research. V.~11. P.~2635--2670. 2010.
\bibitem{kingma2014adam} Kingma, Diederik P., Ba, Jimmy. Adam: A Method for Stochastic Optimization. arXiv preprint arXiv:1412.6980. 2014.
\bibitem{wilson2017marginal} Wilson, Ashia C., Roelofs, Rebecca, Stern, Mitchell, Srebro, Nathan, Recht, Benjamin. The Marginal Value of Adaptive Gradient Methods in Machine Learning. Advances in Neural Information Processing Systems. V.~30. 2017.
\bibitem{zhang2017understanding} Zhang, Chiyuan, Bengio, Samy, Hardt, Moritz, Recht, Benjamin, Vinyals, Oriol. Understanding deep learning (still) requires rethinking generalization. Communications of the ACM. V.~64, N~3. P.~107--115. 2021.
\bibitem{arora2018stronger} Arora, Sanjeev, Ge, Rong, Neyshabur, Behnam, Zhang, Yi. Stronger Generalization Bounds for Deep Nets via a Compression Approach. Proceedings of the 35th International Conference on Machine Learning. V.~80. P.~254--263. PMLR. 2018.
\bibitem{hanneke2016optimal} Hanneke, Steve. The optimal sample complexity of PAC learning. Journal of Machine Learning Research. V.~17, N~1. P.~1319--1333. 2016.
\bibitem{lecun1989optimal} LeCun, Yann, Denker, John, Solla, Sara. Optimal Brain Damage. Advances in Neural Information Processing Systems. V.~2. 1989.
\bibitem{han2015learning} Han, Song, Pool, Jeff, Tran, John, Dally, William. Learning both Weights and Connections for Efficient Neural Networks. Advances in Neural Information Processing Systems. V.~28. 2015.
\bibitem{li2016pruning} Li, Hao, Kadav, Asim, Durdanovic, Igor, Samet, Hanan, Graf, Hans Peter. Pruning Filters for Efficient ConvNets. arXiv preprint arXiv:1608.08710. 2017.
\bibitem{he2017channel} He, Yihui, Zhang, Xiangyu, Sun, Jian. Channel pruning for accelerating very deep neural networks. International Conference on Computer Vision. P.~1389--1397. 2017.
\bibitem{wang2019picking} Wang, Chaoqi, Zhang, Guodong, Grosse, Roger. Picking Winning Tickets Before Training by Preserving Gradient Flow. International Conference on Learning Representations. 2020.
\bibitem{rastegari2016xnor} Rastegari, Mohammad, Ordonez, Vicente, Redmon, Joseph, Farhadi, Ali. XNOR-Net: ImageNet Classification Using Binary Convolutional Neural Networks. ECCV. 2016.
\bibitem{hubara2017quantized} Hubara, Itay, Courbariaux, Matthieu, Soudry, Daniel, El-Yaniv, Ran, Bengio, Yoshua. Quantized neural networks: training neural networks with low precision weights and activations. Journal of Machine Learning Research. V.~18, N~1. P.~6869--6898. 2017.
\bibitem{jacob2018quantization} Jacob, Benoit, Kligys, Skirmantas, Chen, Bo, Zhu, Menglong, Tang, Matthew, Howard, Andrew, Adam, Hartwig, Kalenichenko, Dmitry. Quantization and training of neural networks for efficient integer-arithmetic-only inference. Conference on Computer Vision and Pattern Recognition. P.~2704--2713. 2018.
\bibitem{zhou2016dorefa} Zhou, Shuchang, Wu, Yuxin, Ni, Zekun, Zhou, Xinyu, Wen, He, Zou, Yuheng. DoReFa-Net: Training Low Bitwidth Convolutional Neural Networks with Low Bitwidth Gradients. CoRR. V.~abs/1606.06160. 2016.
\bibitem{wang2019haq} Wang, Kuan, Liu, Zhijian, Lin, Yujun, Lin, Ji, Han, Song. HAQ: Hardware-Aware Automated Quantization With Mixed Precision. IEEE Conference on Computer Vision and Pattern Recognition. 2019.
\bibitem{gunasekar2018implicit} Gunasekar, Suriya, Woodworth, Blake, Bhojanapalli, Srinadh, Neyshabur, Behnam, Srebro, Nathan. Implicit Regularization in Matrix Factorization. arXiv preprint arXiv:1705.09280. 2017.
\bibitem{neyshabur2017geometry} Neyshabur, Behnam, Tomioka, Ryota, Salakhutdinov, Ruslan, Srebro, Nathan. Geometry of Optimization and Implicit Regularization in Deep Learning. arXiv preprint. 2017.
